---
title: "NYC Group TED Talks"
output: html_document
---
# used kernel https://www.kaggle.com/mikaelhuss/r-clone-of-ted-data-analysis-notebook?scriptVersionId=1614520

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(anytime) # For converting UNIX timestamps
library(lubridate)
library(dplyr)
library(corrplot)
library(ggplot2)
library(plyr)
library(RJSONIO)
library(tm)
library(SnowballC)
library(wordcloud)
library(igraph)
library(reshape)
library(readr)
```

```{r}
month_order = c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul', 'Aug', 'Sep', 'Oct', 'Nov', 'Dec')
day_order = c('Mon', 'Tue', 'Wed', 'Thu', 'Fri', 'Sat', 'Sun')
```

```{r}
df <- read_csv("C:/AT/tedtalks/ted_main.csv")
colnames (df)

# for reordering data
df = df[, c('name', 'title', 'description', 'main_speaker', 'speaker_occupation', 'num_speaker', 'duration', 'event', 'film_date', 'published_date', 'comments', 'tags', 'languages', 'ratings', 'related_talks', 'url', 'views')]

# for converting unix dates
df$film_date = anydate(df$film_date)
df$published_date = anydate(df$published_date)
head(df)
nrow(df)

```
# for displaying the top 20 viewed talks
```{r}
pop_talks = df[, c("title", "main_speaker", "views", "film_date")] %>% arrange(desc(views)) %>% head(20)
pop_talks
```
# for visualizing the top 20 viewed talks
```{r}
pop_talks$abbr <- pop_talks$main_speaker %>% as.character() %>% substr(0,3)
ggplot(pop_talks, aes(x=reorder(abbr, views), y=views, fill=abbr)) +
  geom_bar(stat = 'identity') +
  guides(fill=FALSE) + 
  labs(x="abbr")
```
# for adding the histogram 
```{r}

plot(density(df$views))
plot(density(df$views[df$views<0.4e7]))
summary(df$views)
# for summarizing the comments
summary(df$comments)
plot(density(df$comments))
# since most of the talks have less tahn 300 comments we replot the chart
plot(density(df$comments[df$comments < 300]))

```

# for visualizing the relation between views and comments
```{r}
ggplot(df, aes(x=views, y=comments)) + 
  geom_point()
# for the calculation of correlation btw views and comments
cor(df[, c("views", "comments")])

# let's check all the correlation btw numeric fields, which was not analyzed on the kernel we used as a basis
for_cor = cor(df[, c("views", "comments","duration","num_speaker","languages")])
M <- cor(for_cor)
View(M)
corrplot(M,method = "circle")
corrplot(M,method = "number")
corrplot(M,method = "shade")
corrplot(M,method = "color")
corrplot(M,method = "pie")
corrplot(M,method = "square")
summary(for_cor)

# Visualizing many possible relations
ggplot(df, aes(x=languages, y=views)) + geom_point()
ggplot(df, aes(x=languages, y=duration)) + geom_point()
ggplot(df, aes(x=comments, y=views)) + geom_point()
ggplot(df, aes(x=num_speaker, y=views)) + geom_point()
ggplot(df, aes(x=duration, y=views)) + geom_point()
```

# for displaying no of talks by years
```{r}
df$year <- year(df$film_date)
year_df <- data.frame(table(df$year))
colnames(year_df) <- c("year", "talks")
ggplot(year_df, aes(x=year, y=talks, group=1)) + geom_line() + geom_point() + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
# for listing the 15 most popular speakers
```{r}
speaker_df <- data.frame(table(df$main_speaker))
colnames(speaker_df) <- c("main_speaker", "appearances")
speaker_df <- speaker_df %>% arrange(desc(appearances))
head(speaker_df, 15)
```
# to find the most popular occupations among speakers
```{r}
occupation_df <- data.frame(table(df$speaker_occupation))
colnames(occupation_df) <- c("occupation", "appearances")
occupation_df <- occupation_df %>% arrange(desc(appearances))
head(occupation_df, 10)

# to plot the occupatins on a barchart

ggplot(head(occupation_df,10), aes(x=reorder(occupation, appearances), 
                                   y=appearances, fill=occupation)) + 
    geom_bar(stat="identity") + guides(fill=FALSE)
```
# to find the most popular occupations per event which was not analyzed on the kernel we used as a basis
```{r}
occup_dfLast <- data.frame(table(df$event, df$speaker_occupation))
colnames(occup_dfLast) <- c("event", "speaker_occupation", "appearances")
occup_dfLast <- occup_dfLast %>% arrange(desc(appearances))
View(occup_dfLast)

# to plot the occupatins on a barchart

ggplot(head(occup_dfLast,10), aes(x=reorder(speaker_occupation, appearances), y=appearances, fill=speaker_occupation)) + geom_bar(stat="identity") + guides(fill=FALSE)
```

# Number of speakers by talks
```{r}
table(df$num_speaker)
# Let's list the 3 talks which had 4 speakers
df[df[,'num_speaker'] == 4, c('title', 'description', 'main_speaker', 'event')]

```
# No of talks by events
```{r}
event_df <- data.frame(table(df$event))
colnames(event_df) <- c("event", "talks")
event_df <- event_df %>% arrange(desc(talks))
head(event_df, 10)
```

# Languages
```{r}
summary(df$languages)

# Does more languages cause more views? There is a medium correlation rat e of 0,38 as we also analyzed in an earlier section in which we checked all correlation btw variables
ggplot(df, aes(x=languages, y=views)) + geom_point()
cor(df[, c("languages","views")])
```

# Distribution of talk durations
```{r}
df$duration <- df$duration/60
summary(df$duration)
# Since the average talks aveage less than 14 mins we would like to plot the talks shorter than 20 mins
ggplot(df[df$duration<20,], aes(x=duration, y=views)) + geom_point()
```

```{r}
df2 <- read.csv("C:/AT/tedtalks/transcripts.csv", stringsAsFactors = FALSE)
head (df2)
nrow (df2)

df3 <- base::merge(df, df2, by="url")
head(df3)

wc <- function(x){
  #x <- as.character(x)
  words <- strsplit(x[[1]], split="\\s+")
  return(length(words[[1]]))
}

df3$wc <- sapply(df3$transcript, wc)
summary(df3$wc)

# word cloud

texts <- df3$transcript
#texts <- iconv(texts, to = "utf-8")
corpus <- Corpus(VectorSource(texts))
corpus <- tm_map(corpus, PlainTextDocument)
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeWords, stopwords('english'))
corpus <- tm_map(corpus, stemDocument)
corpus <- tm_map(corpus, removeWords, c("and", "this", "there")) 
corpus <- Corpus(VectorSource(corpus))
dtm <- TermDocumentMatrix(corpus)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 10)
d <- d[-which(d$word %in% c("and","this","that")),]
set.seed(1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
          
```
  
